Theoretical aspects in gravity modelling

### 2018-05-10 manuscript/letter.tex
Some more changes to the introduction
Some more rewording of a few phases.

The \textit{gravity vector} is the sum of the gravitational and centrifugal
accelerations felt by a body at rest on the Earth's surface.
Its intensity is what is geoscientists call \textit{gravity}
\citep{heiskanen-moritz1967, hofmann-wellenhof-moritz2005}.
When measured on moving platforms (e.g., airplanes,
helicopters, marine vessels), there are additional
non-gravitational accelerations due to the vehicle motion,
such as Coriolis acceleration and high-frequency vibrations
\citep{glennie-etal2000,nabighian-etal2005-grav,baumann-etal2012}.
Geodesists use gravity measurements to estimate the Geoid \citep{li2001}
whereas geophysicists use gravity to estimate the Earth's
internal density distribution.
Hence, geophysicists are usually only interested
in the gravitational component of the observed gravity
because it is the part that reflects the Earth's internal density distribution.

The first step toward isolating the gravitational component
is to remove the effects of vehicle motion, Earth tides, instrumental drift,
and barometric pressure changes, among others.
If these effects are properly removed, the resultant
observations can be considered to be solely the sum of the
centrifugal acceleration due to the Earth's rotation and
the gravitational acceleration produced by
the internal density distribution of the whole Earth.
The isolation of this particular gravitational component
and its subsequent use for estimating density
distributions related to geological structures in subsurface
are the main goals of applied gravimetry \citep{blakely1996}.
The computation of the gravitational effect produced by
the geological structures is commonly known in geophysics as
\textit{gravity modelling}.
This term is different from \textit{gravity field modelling}, which
is commonly used in geodesy to denote the mathematical characterization of the
gravity field in local, regional, or global scales (e.g., spherical harmonic
analysis).

>>>>

The \textit{gravity vector} is the sum of the gravitational and centrifugal
accelerations felt by a body at rest on the Earth's surface.
Its intensity is what is geoscientists call \textit{gravity}
\citep{heiskanen-moritz1967, hofmann-wellenhof-moritz2005}.
When measured on moving platforms (e.g., airplanes,
helicopters, marine vessels), there are additional
non-gravitational accelerations due to the motion of the vehicle,
such as the Coriolis acceleration and high-frequency vibrations
\citep{glennie-etal2000,nabighian-etal2005-grav,baumann-etal2012}.
Geodesists use gravity measurements to estimate the Geoid \citep{li2001}
whereas geophysicists use gravity to estimate the Earth's
internal density distribution.
Hence, geophysicists are usually only interested
in the gravitational component of the observed gravity
because that is what that reflects the Earth's internal density distribution.

The first step toward isolating the gravitational component
is to remove the effects of vehicle motion, Earth tides, instrumental drift,
and barometric pressure changes, among others.
If these effects are properly removed,
the resultant observations are considered to be solely
the sum of the centrifugal acceleration due to the Earth's rotation and
the gravitational acceleration produced by
the internal density distribution of the whole Earth.
The isolation of this particular gravitational component,
and its subsequent use for estimating density
distributions related to geological structures in subsurface,
are the main goals of applied gravimetry \citep{blakely1996}.
The computation of the gravitational effect produced by
the geological structures is known in geophysics as
\textit{gravity modelling}.
Not to be confused with \textit{gravity field modelling}, which
is commonly used in geodesy to denote the mathematical characterization of the
gravity field in local, regional, or global scales (e.g., spherical harmonic
analysis).
